Methodology for Assessing the State of the Practice for Domain X

### 2020-11-20 StateOfPractice/Methodology/Methodology.tex
moved traceability from methodology to questions to developers
Revisions to candidate software indentification section

\begin{enumerate}
\item What artifacts are present in current software packages? 
\item What tools are used by current software packages?
\item What principles, processes, and methodologies are used in the development
  of current software packages?
\item What are the pain points for developers working on research software
  projects?  What aspects of the existing processes, methodologies and tools do
  they consider as potentially needing improvement?  How should processes,
  methodologies and tools be changed to improve software development and
  software quality?
\item For research software developers, what specific actions are taken to
  address the following:
\begin{enumerate}
\item usability \pmi{question to developers 11}
\item traceability \pmi{question to developers 3}
\item modifiability \pmi{question to developers 9}
\item maintainability \pmi{question to developers 9}
\item correctness \pmi{question to developers 8}
\item understandability \pmi{question to developers 10}
\item unambiguity \pmi{question to developers 12}
\item reproducibility \pmi{question to developers 13}
\item visibility/transparency \pmi{question to developers 3}
\end{enumerate} 
\item How does software designated as high quality by this methodology compare
  with top rated software by the community?
\end{enumerate}

@@

A domain of research software must be identified. Research software is defined
in this exercise as ``software that is used to generate, process or analyze
results that [are intended] to appear in a publication''
\citep{hettrick2014uk}. The chosen domain must have the following properties:

\begin{enumerate}
\item The domain must have a well-defined, stable theoretical
  underpinning. Standard textbooks, preferably understandable by an upper
  undergraduate student, is a good sign of this.
\item There must be a community of people studying the domain.
\item The software packages must have open source options.
\item A preliminary search, or discussion with experts, suggests that there will
  be numerous, at least about 15, candidate software packages in the domain that
  qualify as `research software'.
\end{enumerate}

Some examples of domains that fit these criteria are finite element analysis,
quantum chemistry, seismology, as well as mesh generators and processors. These
are described in \citep{szabo1996finite}, \citep{veryazov20042molcas},
\citep{SmithEtAl2018} and \citep{smith2016state}, respectively.

@@

The candidate software can be found through search engine queries targeting
authoritative lists of software from the domain, such as lists on GitHub and
swMATH, and by searching domain related publications. Domain experts are also
asked for their suggestions and are asked to review the list. The candidate
software should have the following properties:

\begin{enumerate}
\item Major function(s) must fall within the identified domain.
\item Must have viewable source code.
\item Ideally have a git repository or ability to gather empirical measures
  found in Section \ref{SecEmpiricalMeasures}.
\item The software cannot be marked as incomplete or in an initial development
  phase.
\end{enumerate}

>>>>

\begin{enumerate}
\item What artifacts are present in current software packages? 
\item What tools are used by current software packages?
\item What principles, processes, and methodologies are used in the development
  of current software packages?
\item What are the pain points for developers working on research software
  projects?  What aspects of the existing processes, methodologies and tools do
  they consider as potentially needing improvement?  How should processes,
  methodologies and tools be changed to improve software development and
  software quality?
\item For research software developers, what specific actions are taken to
  address the following:
\begin{enumerate}
\item usability
\item traceability
\item modifiability
\item maintainability
\item correctness
\item understandability
\item unambiguity
\item reproducibility
\item visibility/transparency
\end{enumerate} 
\item How does software designated as high quality by this methodology compare
  with top rated software by the community?
\end{enumerate}

@@

A domain of research software must be identified. Research software is defined
in this exercise as ``software that is used to generate, process or analyze
results that [are intended] to appear in a publication'' \citep{hettrick2014uk}
in a scientific or engineering context.  Research software is a more general
term that covers what is often called scientific computing.  To be applicable
for the methodology described in this document, the chosen domain must have the
following properties:

\begin{enumerate}
\item The domain must have well-defined and stable theoretical underpinning.  A
  good sign of this is the existance of standard textbooks, preferably
  understandable by an upper year undergraduate student.
\item There must be a community of people studying the domain.
\item The software packages must have open source options.
\item A preliminary search, or discussion with experts, suggests that there will
  be numerous, at least 15, candidate software packages in the domain that
  qualify as `research software'.
\end{enumerate}

Some examples of domains that fit these criteria are finite element analysis
\citep{szabo1996finite}, quantum chemistry \citep{veryazov20042molcas},
seismology \citep{SmithEtAl2018}, as well as mesh generators
\citep{smith2016state}.

@@

Once the domain of interest is identified, the candidate software for measuring
can be found through search engine queries targeting authoritative lists of
software.  Potential places to search include \href{https://github.com/}
{GitHub}, \href{https://swmath.org/} {swMATH} and domain related publications,
such as review articles. Domain experts are also asked for their suggestions and
are asked to review the initial draft of the software list.

When forming the list and reviewing the candidate software the following
properties should be considered:

\begin{enumerate}
\item The software functionality must fall within the identified domain.
\item The source code must be viewable.
\item The empirical measures listed in Section \ref{SecEmpiricalMeasures} should
  ideally be available, which implies a preference for GitHub repositories.
\item The software cannot be marked as incomplete or in an initial development
  phase.
\end{enumerate}
